Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
Add result of package survey to paper (8 out of 23 have tests)
More survey results included for now (we can always strip this)

Haskell programmers, however, is apt to rely on the type system too much
and tend not to write test code.
For example, Haskell Platform 2011.4.0.0 contains
TBD packages but TBD of them have no test code.
Lacking test code also means that typical usage examples are not provided.

>>>>

Haskell programmers, however, is apt to rely on the type system too
much and tend not to write test code.  For example, the Haskell
Platform 2011.4.0.0 contains 23 packages (not counting the 19 core
libraries that come with GHC), but only 8 of them a test suite (5
provide example code, 10 have no tests nor examples).  Lacking test
code also means that typical usage examples are not provided.
